MSDS 6372 Project 1 Objective 1

### 2020-02-07 Codebook/MSDS6372.Project.O1.Rmd

#### Log-log model
- Due to lack of linearity trying to transform the independent variables to see if we can surface a linear relationship
```{r created logged independent variables}
log.indep.nyc <- log.nyc %>% mutate(lreviews=log(number_of_reviews))
log.indep.nyc <- log.indep.nyc %>% mutate(lnights=log(minimum_nights))
log.indep.nyc <- log.indep.nyc %>% mutate(llistings=log(calculated_host_listings_count))
invisible(log.indep.nyc)

@@

#### Model selection attempts
```{r forward selection model}
nyc.fwd = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers, method="forward",nvmax=20)
summary(nyc.fwd)$adjr2
summary(nyc.fwd)$rss
summary(nyc.fwd)$bic
```

>>>>

#### Log-log model
- Due to lack of linearity trying to transform the independent variables to see if we can surface a linear relationship

```{r created logged independent variables}
log.indep.nyc <- log.nyc %>% mutate(lreviews=log(number_of_reviews))
log.indep.nyc <- log.indep.nyc %>% mutate(lnights=log(minimum_nights))
log.indep.nyc <- log.indep.nyc %>% mutate(llistings=log(calculated_host_listings_count))
invisible(log.indep.nyc)

@@

#### Model selection attempts

```{r forward selection model}
nyc.fwd = regsubsets(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers, method="forward",nvmax=20)
summary(nyc.fwd)$adjr2
summary(nyc.fwd)$rss
summary(nyc.fwd)$bic
```
